Measurement of deeply virtual Compton scattering off Helium-4

### 2017-09-19 eg6-letters/long-paper/prc-dvcshelium.tex
some fixing
added the abstract

\documentclass[aps,prc,preprint,superscriptaddress]{revtex4-1}

@@

%Title of paper
\title{Measurement of deeply virtual Compton scattering off helium-4}

% repeat the \author .. \affiliation  etc. as needed
% \email, \thanks, \homepage, \altaffiliation all apply to the current
% author. Explanatory text should go in the []'s, actual e-mail
% address or url should go in the {}'s for \email and \homepage.
% Please use the appropriate macro foreach each type of information

% \affiliation command applies to all authors since the last
% \affiliation command. The \affiliation command should follow the
% other information
% \affiliation can be followed by \email, \homepage, \thanks as well.
\author{CLAS et al.}
%\email[]{Your e-mail address}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
\affiliation{JLab et al.}

%Collaboration name if desired (requires use of superscriptaddress
%option in \documentclass). \noaffiliation is required (may also be
%used with the \author command).
%\collaboration can be followed by \email, \homepage, \thanks as well.
\collaboration{CLAS Collaboration}
\noaffiliation

@@

\begin{abstract}
% insert abstract here
\end{abstract}

@@

\end{document}
%
% ****** End of file apstemplate.tex ******

>>>>

\documentclass[aps,prc,preprint,superscriptaddress]{revtex4}

@@

%Title of paper
\title{Measurement of deeply virtual Compton scattering off Helium-4}

\input author_list.tex

@@

\begin{abstract}
Measurements of the beam-spin asymmetry in the deeply virtual Compton 
scattering off $^4$He using the CEBAF Large Acceptance Spectrometer (CLAS) are 
reported. A 6 GeV longitudinally polarized electron beam was incident on a 
pressurized $^4$He gaseous target to study the partonic structure of the 
nucleus and the bound nucleons. To ensure the exclusivity of the reactions, 
CLAS was upgraded with a radial time projection chamber to detect the 
low-energy recoiling $^4$He nuclei and an inner calorimeter to extend the 
photon detection acceptance to very forward angles. Our results confirm the 
theoretically predicted enhancement of the coherent 
($e^4$He~$\to~e'$$^4$He$'\gamma'$) beam-spin asymmetries compared to those 
observed on the free proton, while the incoherent 
($e^4$He~$\to~e'$p$'\gamma'$X$'$) asymmetries exhibit a 30$\%$ suppression.  
From the coherent data, we were able to extract, in a model-independent way, 
the real and imaginary parts of the only $^4$He Compton form factor, $\cal 
H_A$, leading the way toward 3D imaging of the partonic structure of nuclei.

\end{abstract}

@@

\end{document}
